Julia for HPC: In Situ Data Analysis with Julia for Climate Simulations at Large Scale

### 2023-09-18 paper/paper.tex
Update paper.tex

\usepackage{amsmath}
\usepackage[ruled,vlined]{algorithm2e}
%\usepackage{algorithm, algorithmic}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, height=3.5cm]{infra.png}
    \caption{Overall infrastructure design.}
    \label{fig:infra}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{ssw_results.png}
    \caption{Generalized extreme value (GEV) model parameter estimates at the end of one simulation year for the non-SSW time periods across the continental United States (coast line denoted with black points). Top: location parameter $\mu$, which shows notable spatial patterns over the Atlantic Ocean and Gulf of Mexico; in addition, a band of lower $\mu$ values appears to stretch through the Midwest region. Bottom: scale parameter $\beta$, which has less smooth spatial structure, but some similarities to the top figure in terms of lower values over bodies of water and through the Midwest region.}
    \label{fig:ssw_results}
\end{figure}

\subsection{PCA Results}
Over the one-year simulation run, we extracted the top three spatial principal components of the surface temperature variable using the TributaryPCA method.
Figure \ref{fig:pca_results} shows spatial plots of these three principal components. 
Each component indicates a different spatial pattern of warming (red color) and cooling (blue color) extracted from the simulation data.
In particular, the first component indicates cooler temperatures away from the equator. 
The second component indicates warming across much of the Eastern hemisphere, with cooling in the Americas and parts of Africa. 
The third component indicates cooling in Africa and Europe with warming elsewhere.
While these components were extracted from a fairly short simulation run, the results demonstrate the ability of TributaryPCA to extract important climate patterns while running in a distributed in situ environment, without saving any raw data for post-processing.
\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{insitu_pca.png}
    \caption{First three spatial principal components obtained by in situ TributaryPCA method. Within each component, white color indicates no change to surface temperature, while blue indicates colder and red indicates hotter temperatures. The first principal component appears to indicate mild tropical warming with cooling away from the equator. The second principal component indicates warming in much of the Eastern hemisphere and cooling in Africa and the Americas, while the third component indicates primarily cooling in Africa and Europe.}
    \label{fig:pca_results}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, height=5.5cm]{ssw_break.pdf}
    \caption{Execution time breakdown for the SSW\_GEV in situ analysis.}
    \label{fig:ssw_break}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, height=5.5cm]{pca_break.pdf}
    \caption{Execution time breakdown for the PCA in situ analysis.}
    \label{fig:pca_break}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, height=5.5cm]{ssw_trend.pdf}
    \caption{Execution time trends of the SSW\_GEV in situ analysis and the EAM component.}
    \label{fig:ssw_trend}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, height=5.5cm]{pca_trend.pdf}
    \caption{Execution time trends of the PCA in situ analysis and the EAM component.}
    \label{fig:pca_trend}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, height=6cm]{ssw_outliers.pdf}
    \caption{Execution time of MPI ranks for the SSW\_GEV in situ analysis.}
    \label{fig:ssw_outliers}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, height=6cm]{pca_outliers.pdf}
    \caption{Execution time of MPI ranks for the PCA in situ analysis.}
    \label{fig:pca_outliers}
\end{figure}

>>>>

\usepackage{amsmath}
%\usepackage[ruled,vlined]{algorithm2e}
\usepackage{algorithm, algorithmic}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, height=3.5cm]{figures/infra.png}
    \caption{Overall infrastructure design.}
    \label{fig:infra}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{figures/ssw_results.png}
    \caption{Generalized extreme value (GEV) model parameter estimates at the end of one simulation year for the non-SSW time periods across the continental United States (coast line denoted with black points). Top: location parameter $\mu$, which shows notable spatial patterns over the Atlantic Ocean and Gulf of Mexico; in addition, a band of lower $\mu$ values appears to stretch through the Midwest region. Bottom: scale parameter $\beta$, which has less smooth spatial structure, but some similarities to the top figure in terms of lower values over bodies of water and through the Midwest region.}
    \label{fig:ssw_results}
\end{figure}

\subsection{PCA Results}
Over the one-year simulation run, we extracted the top three spatial principal components of the surface temperature variable using the TributaryPCA method.
Figure \ref{fig:pca_results} shows spatial plots of these three principal components. 
Each component indicates a different spatial pattern of warming (red color) and cooling (blue color) extracted from the simulation data.
In particular, the first component indicates cooler temperatures away from the equator. 
The second component indicates warming across much of the Eastern hemisphere, with cooling in the Americas and parts of Africa. 
The third component indicates cooling in Africa and Europe with warming elsewhere.
While these components were extracted from a fairly short simulation run, the results demonstrate the ability of TributaryPCA to extract important climate patterns while running in a distributed in situ environment, without saving any raw data for post-processing.
\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{figures/insitu_pca.png}
    \caption{First three spatial principal components obtained by in situ TributaryPCA method. Within each component, white color indicates no change to surface temperature, while blue indicates colder and red indicates hotter temperatures. The first principal component appears to indicate mild tropical warming with cooling away from the equator. The second principal component indicates warming in much of the Eastern hemisphere and cooling in Africa and the Americas, while the third component indicates primarily cooling in Africa and Europe.}
    \label{fig:pca_results}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, height=5.5cm]{figures/ssw_break.pdf}
    \caption{Execution time breakdown for the SSW\_GEV in situ analysis.}
    \label{fig:ssw_break}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, height=5.5cm]{figures/pca_break.pdf}
    \caption{Execution time breakdown for the PCA in situ analysis.}
    \label{fig:pca_break}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, height=5.5cm]{figures/ssw_trend.pdf}
    \caption{Execution time trends of the SSW\_GEV in situ analysis and the EAM component.}
    \label{fig:ssw_trend}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, height=5.5cm]{figures/pca_trend.pdf}
    \caption{Execution time trends of the PCA in situ analysis and the EAM component.}
    \label{fig:pca_trend}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, height=6cm]{figures/ssw_outliers.pdf}
    \caption{Execution time of MPI ranks for the SSW\_GEV in situ analysis.}
    \label{fig:ssw_outliers}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth, height=6cm]{figures/pca_outliers.pdf}
    \caption{Execution time of MPI ranks for the PCA in situ analysis.}
    \label{fig:pca_outliers}
\end{figure}
